### 2022-01-26 sections/conclusion.tex
updating EB comments

%-------------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%-------------------------------------------------------------------------------

A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented. FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction, while the decay according to SM. The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$. The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.

Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Tab~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$). The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.

>>>>

%-------------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%-------------------------------------------------------------------------------
A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented. FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction, while the decay according to SM. The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$. The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.

Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$). The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.

### 2022-01-26 sections/introduction.tex
updating EB comments

Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today. However there are still chances to find new physics improving the sensitivity of previous searches. The presence of flavour-changing neutral-current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) is still an active topic. Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions could manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}. The $t\to u/c+H$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}. 
%such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
%interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
%Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
%As a result, the SM predictions for the $t \to Hq$ branching 
%ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) with or without the flavour violation,
%of type I, with explicit flavour conservation,
%and of type II, such as
the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
%While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
%the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
Therefore, an observation of this decay would be a clear evidence for new physics. The $tqH$ interaction could also potentially open up more
Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
which could be interesting for future studies.

@@

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

>>>>

Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today. However there are still chances to find new physics improving the sensitivity of previous searches. The presence of flavour-changing neutral-current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) is still an active topic. Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
such interactions could manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}. The $t\to u/c+H$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}. 
%such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
%interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
%Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
%As a result, the SM predictions for the $t \to Hq$ branching 
%ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) with or without the flavour violation,
%of type I, with explicit flavour conservation,
%and of type II, such as
the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
%While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
%the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
Therefore, an observation of this decay would be a clear evidence for new physics.
%The $tqH$ interaction could also potentially open up more
%Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
%which could be interesting for future studies.

@@

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$ with a small $\BR(t\to Hq)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

### 2022-01-26 sections/strategy_Htautau.tex
updating EB comments

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} and~\ref{tab:importance_xTFW} and defined in the following:

>>>>

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}, as defined in the following:
